\setstretch{1}
\setlength{\parskip}{\baselineskip}

\section{Introduction}
The increasing complexity of modern electronic circuits demands highly efficient, accurate, and scalable simulation tools. This thesis introduces a newly developed high-performance SPICE-level CAD simulator designed to compete with established industry standards such as HSPICE, LTSPICE, and NGSPICE. The primary objective of this tool is to provide a reliable and extensible platform capable of analyzing complex electronic circuit topologies in both academic and professional environments.

To achieve these goals, the simulator's architecture is strategically divided into several distinct, cohesive modules:
\begin{enumerate}
    \item \textbf{Netlist Parser:} Responsible for reading and interpreting the circuit description. It is subdivided into tasks including a lexical analyzer (tokenizer), a syntax parser, parameter and model extractors, data type definitions, error handling, and the management of control blocks (e.g., \texttt{.end}, \texttt{.op}, and \texttt{.ac}).
    \item \textbf{Mathematical Modeling:} Translates the physical components into mathematical representations using the Modified Nodal Analysis (MNA) methodology. This module supports a wide array of devices including BJTs, MOSFETs, JFETs, inductors, capacitors, diodes, resistors, and various controlled sources (CCCS, CCVS, VCCS, VCVS).
    \item \textbf{Simulator Engine (Solver):} The computational core of the tool. It comprises an Analysis Control Manager for high-level orchestration, a Linear Solver Interface for handling different simulation steps (AC, DC, DC Sweep, Transient), a Nonlinear Solver utilizing the Newton-Raphson method, convergence monitoring mechanisms (managing tolerances like ABSTOL and RELTOL), and performance optimization strategies. A key technical decision in this module is the prioritization of the KLU library for highly efficient, circuit-specific sparse matrix operations.
    \item \textbf{Post-Processing:} A comprehensive simulation workflow built around a WaveformDB layer. This layer feeds three parallel subsystems: a Measurement Engine featuring a \texttt{.meas} parser for automated signal measurements, a PlotEngine utilizing an ImPlotAdapter for interactive waveform visualization, and a Calculator with an Expression Evaluator for user-defined computations. The final waveform outputs are rendered using Gnuplot.
    \item \textbf{Output Generation:} Structured logging and data output to capture the results and performance metrics of the simulation.
\end{enumerate}

This chapter sets the stage for a detailed exploration of each of these modules, outlining the challenges encountered and the robust solutions implemented to deliver a professional-grade CAD tool.

\section{Thesis Organization}
The remainder of this thesis is structured as follows: Chapter 2 reviews the related literature in circuit simulation. Chapter 3 details the overall system architecture. Chapters 4 through 7 delve into the specific implementations of the Netlist Reader, Mathematical Modelling, Simulation Engine, and Post-Processing modules, respectively. Chapter 8 presents benchmarking results. Finally, Chapter 9 concludes the thesis and outlines directions for future work.
